```{r}
library(knitr)
library(rjson)
library(dplyr)
```


## Tue 12 Feb 2019 13:45:42 AEDT
- Youtube api for recommendations 
- https://developers.google.com/youtube/v3/docs/ is the starting point
- possible endpoints to use:
    - https://developers.google.com/youtube/v3/docs/videos for any id gives:


- would we need to consider Channels and possibly playlists? Channels are at https://developers.google.com/youtube/v3/docs/channels, in order to see what they picked as favourited?
- on my HomePage/channel, a lot of recommendations appear. Where did they come from?
- Subscriptions could be an endpoint: https://developers.google.com/youtube/v3/docs/subscriptions
- playlists might have recommendation: https://developers.google.com/youtube/v3/docs/playlists/list




## Thu 14 Feb 2019 11:16:02 AEDT
- Working with the reddit data
- Useful sentiment analysis at https://github.com/aleszu/reddit-sentiment-analysis; also has the python script for getting stuff


## Fri 15 Feb 2019 08:25:36 AEDT
- value of reddit users https://www.cnbc.com/2019/02/11/reddit-users-are-the-least-valuable-of-any-social-network.html
- list of top subreddits https://medium.com/@davis1/the-31-biggest-subreddits-f95c1f1f5e97

    1. funny — 19,895,474 subscribers

    2. AskReddit — 19,510,110

    3. todayilearned — 18,981,496

    4. worldnews — 18,977,231

    5. Science — 18,932,710

    6. pics — 18,886,430

    7. gaming — 18,413,642

    8. IAmA — 18,097,375

    9. videos — 17,973,194

    10. movies — 17,824,982

    11. aww — 17,433,245 pets

    12. Music — 17,051,188

    13. blog — 16,507,239

    14. gifs — 16,321,999

    15. news — 16,218,736

    16. explainlikeimfive — 15,705,452

    17. askscience — 15,634,059

    18. EarthPorn — 15,529,380

    19. books — 14,732,532

    20. television — 14,730,352

- found this paper on reddit https://www.reddit.com/r/science/comments/aqavuw/machine_learning_analysis_of_deleted_content_on/
- saved in ~/archive/ensembles/reddit_deletions_2019.pdf


## Mon 18 Feb 2019 14:26:19 AEDT
-  3 problems for the data sprint:
    1. karma reverse engineering
    2. dynamics of attention -- platforms vs internal; 
    3. moderation effects 


## Wed 20 Feb 2019 09:42:05 AEDT

```{r masterclass}
library(igraph)
library(vosonSML)
library(quanteda)
help.start()

```

